### 2018-01-01 Paper/examples.tex
work in progress
added oscillator schematic

\noindent As discussed earlier in section~\ref{sec:method}, computational cost associated with
L-2 verification is negligible since function evaluations or model realizations obtained during the
screening step could be re-used.
However, since the test problems are computationally inexpensive, we generate an independent
set of samples ($\bm{\theta_i}$) to estimate $\epsilon_{\mbox{\tiny{L-2}}}$ using Eq.~\ref{eq:l2}
in each case.
For the purpose of probabilistic verification, we compare the probability density function of
the observable obtained using PCE's in the full space and the reduced space in the following
test problems. In situations where model runs are computationally expensive, probabilistic verification might
not be feasible.

@@

>>>>

\noindent As discussed earlier in section~\ref{sec:method}, computational cost associated with
L-2 verification is negligible since function evaluations or model realizations obtained during the
screening step could be re-used to estimate $\epsilon_{\mbox{\tiny{L-2}}}$ using Eq.~\ref{eq:l2}.
For the purpose of probabilistic verification, we compare the probability density function of
the observable obtained using PCE's in the full space and the reduced space in the following
test problems. In situations where model runs are computationally expensive, probabilistic verification might
not be feasible.

@@

As discussed earlier in this section, the reduced order PCE's are verified for predictive accuracy in 
a least-squares sense and a probabilistic sense. Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$
based on 50 samples and corresponding function evaluations in the original 7D parameter space
were found to be 0.0551 and 0.0112 for the 4D and 5D PCE's respectively. In other words, the 4D
PCE is accurate within 5.52$\%$ and the 5D PCE is accurate within 1.12$\%$ of predictions based on
the borehole function. It is interesting to note that although the order of convergence in the case of a 5D
PCE is lower (Figure~\ref{fig:conv_bore}), its predictive accuracy is higher than the 4D PCE. A possible
explanation for this observation is that above a certain order of convergence, the uncertainty in $k_w$ 
contributes much more towards predictive accuracy of the reduced order PCE. It is therefore critical
to account for the order of PCE convergence as well as its predictive accuracy for a given application,
as highlighted earlier in section~\ref{sec:method}.

Figure~\ref{fig:pdfcomp_bore} illustrates a comparison of the PDF's of the discharge, $\mathcal{Q}$
obtained by propagating 10$^6$ Monte-Carlo (MC) samples through the 7D PCE in the
original input parameter domain as well as the reduced order PCE's constructed in 4 and 5 dimensions. 
It is evident from this plot, that the PDF's agree quite favorably with each other. Consequently, it can
be said that the reduced order PCE is verified in a probabilistic sense. In other words, the mode as
well as the uncertainty in the observable is reliably captured and predicted by the reduced order PCE.

\subsection{Non-linear Oscillator}
